Affective Uplift During Video Game Play: A Naturalistic Case Study

### 2023-10-19 ms.Rmd
Typos etc

---
title: "Affective Uplift During Video Game Play: A Naturalistic Case Study"
shorttitle: Affective Uplift During Play
leftheader: Affective Uplift During Play
author: 
  - name: Matti Vuorre
    corresponding: yes
    affiliation: "1,2*"
    address: Tilburg University
    email: mjvuorre@uvt.nl
  - name: Nick Ballou
    affiliation: "2*"
  - name: Thomas Hakman
    affiliation: "2"
  - name: Kristoffer Magnusson
    affiliation: "2,3"
  - name: Andrew K. Przybylski
    affiliation: "2"
    address: Oxford Internet Institute
    email: andy.przybylski@oii.ox.ac.uk
affiliation:
  - id: 1
    institution: Tilburg School of Social and Behavioral Sciences, Tilburg University
  - id: 2
    institution: Oxford Internet Institute, University of Oxford
  - id: 3
    institution: Centre for Psychiatry Research, Department of Clinical Neuroscience, Karolinska Institutet, & Stockholm Health Care Services, Region Stockholm, Sweden
authornote: |
  \noindent \textbf{This pre-print is not yet peer-reviewed.} 
  *MV and NB contributed equally to this work.

wordcount: '`r scales::number(wordcountaddin:::word_count("ms.Rmd"), big.mark = ",")`'
bibliography: references.bib
keywords: "video games, well-being, mood, play behavior, telemetry"
csl: apa.csl
floatsintext: yes
linenumbers: no
draft: no
mask: yes
figurelist: no
tablelist: no
footnotelist: no
documentclass: apa7
classoption: doc
output: 
  papaja::apa6_pdf:
    number_sections: false
    keep_tex: true
  papaja::apa6_docx: 
    number_sections: false
editor_options: 
  chunk_output_type: console
---

@@

```{r}
#| label: fig-ct1
#| include: true
#| fig.cap: "Estimated (changes) in mood as a function of session duration. Top: Average mood during a gaming session. Bottom: Change in mood during a session compared to mood at the beginning of a session. Gray ribbons indicate 95\\% confidence bands. We truncated the x-axis at three hours for this figure."
#| fig-height: 3
#| fig-width: 8

@@

@@

# Contributions

\noindent
Conceptualization: MV, AKP\
Data Curation: MV, KM\
Formal Analysis: MV, KM\
Funding Acquisition: AKP, MV, KM\
Methodology: MV, KM\
Project Administration: MV, AKP\
Resources: AKP, MV\
Supervision: AKP, MV\
Validation: KM, MV\
Visualization: MV, KM\
Writing – Original Draft: NB, MV, TH, AKP, KM\
Writing – Review & Editing: MV, NB, TH, AKP, KM\

# Funding information

# Competing interests

# Data accessibility statement

The data and code we used to analyze it are available on GitHub (<https://github.com/digital-wellbeing/pws-prepost>) and archived at Zenodo (<https://zenodo.org/doi/10.5281/zenodo.10021014>). For the full PWS dataset, see @vuorreIntensiveLongitudinalDataset2023.

# Figure titles and legends

## Figure 1.

A. Scatterplots of three participants' (rows) mood responses (pre-play: red; during play: blue) over eight sessions' (columns) durations. B. Histograms of session-mean (C. person-mean) moods before (top) and during (bottom) play sessions. D. Differences in session-mean (E. player-mean) mood differences (during session - pre-play). F. Scatterplot of person-mean mood reports at the beginning (x-axis) and during gameplay sessions (y-axis). Identity line is shown in green, and an exploratory GAM regression line is shown in blue.

## Figure 2.

Estimated (changes) in mood as a function of session duration. Top: Average mood during a gaming session. Bottom: Change in mood during a session compared to mood at the beginning of a session. Gray ribbons indicate 95\% confidence bands. We truncated the x-axis at three hours for this figure.

## Figure 3.

Estimated (changes) in mood as a function of session duration and pre-play mood. Top. Mood for the average player during a gaming session with pre-play mood at 5th, 25th, 50th, and 75th percentiles (columns). Ribbons indicate 95\% confidence. Bottom. Same as above but with change in mood on the y-axis.

>>>>

---
title: "Affective Uplift During Video Game Play: A Naturalistic Case Study"
shorttitle: Affective Uplift During Play
leftheader: Affective Uplift During Play
author: 
  - name: Matti Vuorre
    corresponding: yes
    affiliation: "1,2*"
    address: Tilburg University
    email: mjvuorre@uvt.nl
  - name: Nick Ballou
    affiliation: "2*"
  - name: Thomas Hakman
    affiliation: "2"
  - name: Kristoffer Magnusson
    affiliation: "2,3"
  - name: Andrew K. Przybylski
    affiliation: "2"
    address: Oxford Internet Institute
    email: andy.przybylski@oii.ox.ac.uk
affiliation:
  - id: 1
    institution: Tilburg School of Social and Behavioral Sciences, Tilburg University
  - id: 2
    institution: Oxford Internet Institute, University of Oxford
  - id: 3
    institution: Centre for Psychiatry Research, Department of Clinical Neuroscience, Karolinska Institutet, & Stockholm Health Care Services, Region Stockholm, Sweden
authornote: |
  \noindent \textbf{This pre-print is not yet peer-reviewed.}

  *MV and NB contributed equally to this work.

wordcount: '`r scales::number(wordcountaddin:::word_count("ms.Rmd"), big.mark = ",")`'
bibliography: references.bib
keywords: "video games, well-being, mood, play behavior, telemetry"
csl: apa.csl
floatsintext: yes
linenumbers: no
draft: no
mask: no
figurelist: no
tablelist: no
footnotelist: no
documentclass: apa7
classoption: jou
output: 
  papaja::apa6_pdf:
    number_sections: false
    keep_tex: true
  papaja::apa6_docx: 
    number_sections: false
editor_options: 
  chunk_output_type: console
---

@@

```{r}
#| label: fig-ct1
#| include: true
#| fig.cap: "Estimated (changes) in mood as a function of session duration. Top: Average mood during a gaming session. Bottom: Change in mood during a session compared to mood at the beginning of a session. Gray ribbons indicate 95\\% confidence bands. We truncated the x-axis at three hours for this figure."
#| fig-height: 3
#| fig-width: 5

@@

# Data and Material Availability

The data and code we used to analyze it are available on GitHub (<https://github.com/digital-wellbeing/pws-prepost>) and archived at Zenodo (<https://zenodo.org/doi/10.5281/zenodo.10021014>).

# Author contributions

Conceptualization: MV, AKP\
Data Curation: MV, KM\
Formal Analysis: MV, KM\
Funding Acquisition: AKP, MV, KM\
Methodology: MV, KM\
Project Administration: MV, AKP\
Resources: AKP, MV\
Supervision: AKP, MV\
Validation: KM, MV\
Visualization: MV, KM\
Writing – Original Draft: NB, MV, TH, AKP, KM\
Writing – Review & Editing: MV, NB, TH, AKP, KM\

# Declaration of Conflicting Interests

# Funding

@@
